---
title: "Practical Machine Learning Project"
output: html_document
---
#Executive Summary
Human Acitivity Recognition has emerged as a key research area in the last years. The goal of this project is to use data from accelerometers on the belt, forearm, arm and dumbell of 6 participants to build a model to predict the manner in which they did the exercise.

#Data processing
Let's load the data and create training and testing data partitions:

```{r echo=TRUE}
library(caret)


pmlt<- read.csv("pml-training.csv")

inTrain <- createDataPartition(pmlt$classe, p = 0.7, list=F)
testing <- pmlt[-inTrain,]
training <- pmlt[inTrain,]

```
The dataset has 160 variables and 19622 observations. With str() command, we found many columns were empty which would be discarded from our model:
* Discard empty columns
* Near Zero Variance Covariates
* Non relavent columns
```{r echo=TRUE}
training <- training[ , colSums(is.na(training)) == 0]
nzv <- nearZeroVar(training)
training <- training[-nzv]
training <- subset(training, select=-c(1:6))
```



#Model Fitting
We had performed the below two models fitting against training dataset:
* Naive Bayes Model
* Random Forest Model

```{r echo=TRUE}
fitC1<- trainControl(method = "cv" , number=10)
fit1<- train(training$classe ~ ., data=training, preProcess="pca", method ="nb", trControl=fitC1)
print(fit1)

fitC2 <- trainControl(method="cv", number=10)
fit2 <- train(training$classe ~ ., data=training, preProcess="pca", method="rf", trControl=fitC2)
print(fit2)
```

#Model Selection
Test the model against the testing set to estimate the out of sample error rate:

```{r echo=TRUE}
confusionMatrix(predict(fit1, testing), testing$classe)
confusionMatrix(predict(fit2, testing), testing$classe)
```

Based on the accuracy, Random Forest model is the best for this dataset.

#Prediction on Assignment Data
Applying the Random Forest model to PML testing data:
```{r echo=TRUE}
test <- read.csv("pml-testing.csv")
predict(fit2, test)
```

